\documentclass[12pt]{article}
\date{2023/09/25}
\author{Idris Raja}
\title{Exercise 1.1}
\input{commands}


\begin{document}
\maketitle
\prompt{Put the arguments into standard form}

\original{If we are going to avoid a nuclear war in the next few years, we will
have to adopt strong punitive measures now. But if we adopt such measures, many
nations will be very unhappy. Thus, we are going to avoid a nuclear war in the
next few years only if many nations are going to be unhappy.}

\premise{If we are going to avoid a nuclear war in the next few years, we will have to adopt strong punitive measures now}

\premise{But if we adopt such measures, many nations will be very unhappy}

\conclusion{Thus, we are going to avoid a nuclear war in the next few years only if many nations are going to be unhappy.}

\original {The state will increase its financial support of our university only if the
priorities of the legislature shift in favor of higher education. But if such a
shift were to occur, the people who benefit from other state projects would
complain bitterly. If the state does not increase financial support for the
university, tuition will have to be raised. So, tuition will be raised.}

\premise{The state will increase its financial support of our university only if the priorities of the legislature shift in favor of higher education.}

\premise{But if such a shift were to occur, the people who benefit from other state projects would complain bitterly.}

\premise{ If the state does not increase financial support for the university, tuition will have to be raised.}

\conclusion{So, tuition will be raised.}

\original {If a man is to play some role in society, that role must be determined by
nature or by society. However, if his role is determined by nature, that role
will be the role of the selfish hunter on the make. Hence, either society
determines a role for man, or man will play the role of the selfish hunter
always on the make}

\premise{If a man is to play some role in society, that role must be determined by nature or by society.}

\premise{However, if his role is determined by nature, that role will be the role of the selfish hunter on the make.}

\conclusion{Hence, either society determines a role for man, or man will play the role of the selfish hunter always on the make}

\original{If it is true that 30 out of every 50 college coeds have sexual intercourse
outside marriage, then it is very important to have birth control informa-
tion available from the Student Health Service. It is very important to have
birth control information available from the Student Health Service. Thus,
we know that 30 out of every 50 college coeds have sexual intercourse
outside marriage.}

\premise{If it is true that 30 out of every 50 college coeds have sexual intercourse outside marriage, then it is very important to have birth control information available from the Student Health Service.}

\premise{It is very important to have birth control information available from the Student Health Service.}

\conclusion{Thus, we know that 30 out of every 50 college coeds have sexual intercourse outside marriage.}

\end{document}
