\input{preamble}
\title{Exercise 7.5, Complex statements}
\date{2023/09/27}
\begin{document}
\maketitle

\begin{enumerate}

\begin{statement}{If you pay for it, you can have it.}
\symbol{A}{If you pay for it}
\symbol{B}{You can have it}
\symbolization{A \implies B}
\end{statement}

\begin{statement}{He will pass the course provided he does the exercise.}
\symbol{A}{He does the exercise}
\symbol{B}{He will pass the course}
\symbolization{A \implies B}
\end{statement}

\begin{statement}{Feeding the birds results in having to feed more birds.}
\symbol{A}{Feeding the bird}
\symbol{B}{having to feed more birds}
\symbolization{A \implies B}
\end{statement}

\begin{statement}{The first two paragraphs are clear and concise.}
\symbol{A}{The first two paragraphs are clear}
\symbol{B}{The first two paragraphs are concise}
\symbolization{A \land B}
\end{statement}

\begin{statement}{Eating right is necessary for staying healthy.}
\symbol{A}{Staying healthy}
\symbol{B}{Eating right}
\symbolization{A \implies B}
\end{statement}

\begin{statement}{He aimed at, but still missed, the target.}
\symbol{A}{He aimed at the target}
\symbol{B}{He missed the target}
\symbolization{A \land B}
\end{statement}

\begin{statement}{You do that, and I’m your slave.}
\symbol{A}{You do that}
\symbol{B}{I'm your slave}
\symbolization{A \implies B}
\end{statement}

\begin{statement}{Mary has many black and white cats.}
\symbol{A}{Mary has white cats}
\symbol{B}{Mary has black cats}
\symbol{C}{Mary has black and white cats}
\symbolization{(A \land B) \lor C}
\end{statement}

\begin{statement}{Since I started early, I’ll be done early.}
\symbol{A}{I started early}
\symbol{B}{I'll be done early}
\symbolization{A \therefore B}
\end{statement}

\begin{statement}{I question whether the meal I ate was nutritious.}
\symbol{A}{I question whether the meal I ate was nutritious.}
\symbolization{A}
\end{statement}

\begin{statement}{Sue is dissatisfied with her grades.}
\symbol{A}{Sue is dissatisfied with her grades.}
\symbolization{A}
\end{statement}

\begin{statement}{Tax forms are not as complicated as they once were.}
\symbol{A}{Tax forms are not as complicated as they once were.}
\symbolization{A}
\end{statement}

\begin{statement}{If Graff defeats Seles, and Fernandez defaults, then Graff and Hingis will go to the finals.}
\symbol{A}{Graff defeats Seles}
\symbol{B}{Fernandez defaults}
\symbol{C}{Graff goes to the finals}
\symbol{D}{Hingis goes to the finals}
\symbolization{(A \land B) \implies (C \land D)}
\end{statement}

\begin{statement}{Bacon and eggs will be served only if they run out of pancakes and do not serve sweet rolls.}
\symbol{A}{Bacon and eggs served}
\symbol{B}{run out of pancakes}
\symbol{C}{serve sweet rolls}
    \symbolization{(B \land \neg C) \implies A}
\end{statement}

\begin{statement}{While there is freedom, there is equality, and if there is freedom and equality, then all men are happy.}
\symbol{A}{There is freedom}
\symbol{B}{There is equality}
\symbol{C}{All men are happy}
\symbolization{(A \implies B) \implies C}
\end{statement}

\begin{statement}{While you had cake, I had cherries.}
\symbol{A}{you had cake}
\symbol{B}{I had cherries}
\symbolization{A \land B)}
\end{statement}

\begin{statement}{I cannot tell you any more, but if I am accepted now, then it cannot be enjoyable for me to reflect that some calculation tipped the scale.}
\symbol{A}{I am accepted now}
\symbol{B}{it is enjoyable for me to reflect that some calculation tipped the scale}
\symbolization{A \land \neg B)}
\end{statement}

\begin{statement}{If New York City is in the USA, then if France is north of India, then South Bend is nowhere.}
\symbol{A}{New York City is in the USA}
\symbol{B}{France is north of India}
\symbol{C}{South Bend is nowhere}
\symbolization{A \implies (B \implies C)}
\end{statement}

\begin{statement}{Fakhruddin went east, and if he had only gone west, he would now be here.}
\symbol{A}{Fakhruddin went east}
\symbol{B}{Fakhruddin went west}
\symbol{C}{Fakhruddin would be here}
\symbolization{A \land (B \implies C)}
\end{statement}

\begin{statement}{getting into law school is a necessary condition for becoming rich.}
\symbol{A}{Get into law school}
\symbol{B}{become rich}
\symbolization{B \implies A}
\end{statement}

\begin{statement}{Getting into law school is a sufficient condition for becoming rich.}
\symbol{A}{Get into law school}
\symbol{B}{become rich}
\symbolization{A \implies B}
\end{statement}

\begin{statement}{Getting into law school is a necessary and sufficient condition for becoming rich.}
\symbol{A}{Get into law school}
\symbol{B}{become rich}
\symbolization{A \iff B}
\end{statement}

\begin{statement}{Getting into law school is a sufficient and necessary condition for becoming rich.}
\symbol{A}{Get into law school}
\symbol{B}{become rich}
\symbolization{A \iff B}
\end{statement}

\begin{statement}{Getting into law school is a necessary and sufficient condition for becoming rich and staying bored.}
\symbol{A}{Get into law school}
\symbol{B}{become rich}
\symbol{C}{staying bored}
\symbolization{A \iff (B \land C}
\end{statement}

\begin{statement}{Getting into law school is a necessary and sufficient condition for becoming rich and staying bored, respectively.}
\symbol{A}{Get into law school}
\symbol{B}{become rich}
\symbol{C}{staying bored}
\symbolization{(B \implies A) \land (A \implies C)}
\end{statement}

\begin{statement}{You will graduate if you work hard.}
\symbol{A}{You will graduate}
\symbol{B}{you work hard}
\symbolization{B \implies A}
\end{statement}

\begin{statement}{You will graduate only if you work hard.}
\symbol{A}{You will graduate}
\symbol{B}{you work hard}
\symbolization{A \implies B}
\end{statement}

\begin{statement}{You will graduate if only you work hard.}
\symbol{A}{You will graduate}
\symbol{B}{you work hard}
\symbolization{B \implies A}
\end{statement}

\begin{statement}{You will graduate if and only if you work hard.}
\symbol{A}{You will graduate}
\symbol{B}{you work hard}
\symbolization{B \iff A}
\end{statement}

\begin{statement}{If you have a specific question, then we will relay it to him if he calls.}
\symbol{A}{you have a specific question}
\symbol{B}{he calls}
\symbol{C}{we will relay it to him }
\symbolization{A \implies (B \implies C)}
\end{statement}

\begin{statement}{If the windows are open, we get hot air and outside noise.}
\symbol{A}{windows are open}
\symbol{B}{we get hot air}
\symbol{C}{we get outside noise}
\symbolization{A \implies (B \land C)}
\end{statement}

\begin{statement}{Having both South Vietnam and Laos go would be sufficient for Cambodia’s going.}
\symbol{A}{South Vietnam goes}
\symbol{B}{Laos goes}
\symbol{C}{Cambodia goes}
\symbolization{(A \land B) \implies C)}
\end{statement}

\begin{statement}{Mary visited the team, but if Bill had been there, she would have left.}
\symbol{A}{Mary visited the team}
\symbol{B}{Bill was there}
\symbol{C}{Mary left}
\symbolization{A \land (B \implies C)}
\end{statement}

\begin{statement}{Should the Yankees win the pennant, then if they play Montreal, I would root for Montreal.}
\symbol{A}{Yankees win the pennant}
\symbol{B}{Yankees play Montreal}
\symbol{C}{I root for Montreal}
    \symbolization{ A \land (B \implies C)}
\end{statement}

\begin{statement}{Mary left, and either Bill left or Julie stayed.}
\symbol{A}{Mary left}
\symbol{B}{Bill left}
\symbol{C}{Julie stayed}
    \symbolization{A \land (B \lor C)}
\end{statement}

\begin{statement}{If the news is delayed, and you receive the main selection without having had ten days to notify us, you may return it for credit at our expense.}
\symbol{A}{news is delayed}
\symbol{B}{receive main selection without having ten days to review it}
\symbol{C}{return it for credit at our expense}
\symbolization{(A \land B) \implies C}
\end{statement}

\begin{statement}{In order that man may usefully cooperate and improve the life of the community, there must be freedom to assess and compare views which seem to have validity.}
\symbol{A}{man may usefully cooperate and improve the life of the community}
\symbol{B}{must be freedom to assess and compare views which seem to have validity}
\symbolization{B \implies A}
\end{statement}

\begin{statement}{Pour over ice cubes in an old-fashioned glass and serve with short straws.}
\symbol{NA}{}
\symbolization{Not an argument. Instead it's an imperative statement}
\end{statement}

\begin{statement}{Enjoy your achievements as well as your plans.}
\symbol{NA}{}
\symbolization{Not an argument. Instead it's an imperative statement}
\end{statement}

\begin{statement}{Being a Jew is worth something if you obey God’s laws; but if you don’t, then you are no better off than a heathen.}
\symbol{A}{Being a Jew is worth something}
\symbol{B}{you obey God's laws}
\symbol{C}{you are no better off than a heathen}
\symbolization{(B \implies A) \land (\neg B \implies C)}
\end{statement}

\begin{statement}{You’re damned if you do, and you’re damned if you don’t.}
\symbol{A}{you do}
\symbol{B}{you're damned}
\symbolization{(A \implies B) \land (\neg A \implies B)}
\end{statement}

\begin{statement}{‘If it can be proved that dreams possess a value of their own
    as psychological acts and that wishes are the motive for their construction
    and that experiences of the preceding day provide the immediate material for
    their content, then any theory of dreams which neglects so important a
    procedure of research and accordingly represents dreams as a useless and
    puzzling reaction to somatic stimuli, stands condemned without there being
    any necessity for specific criticism’ (Freud, Interpretation of Dreams).}
\symbol{A}{dreams possess a value of their own as psychological acts}
\symbol{B}{wishes are the motive for dream construction}
\symbol{C}{experiences of the preceding day provide the immediate material for dream content}
\symbol{D}{theory represents dreams as a useless and puzzling reaction to somatic stimuli}
\symbol{E}{condemned without any necessity for specific criticism}
    \symbolization{(A \land B \land C) \implies (D \implies E)}
\end{statement}

\end{enumerate}
\end{document}
