% \input{preamble}
% \date{2023/09/30}
% \begin{document}
% \maketitle

\section{\S 8.1, Arguments and Truth Trees}
\begin{enumerate}

	\begin{statement}{Kennedy, Johnson, and Nixon were all presidents. It is not true that Kennedy
			and Mondale were both presidents. So, it is also not the case that Nixon
			and Mondale were both presidents.}
		\symbol{A}{Kennedy was a president.}
		\symbol{B}{Johnson was a president.}
		\symbol{C}{Nixon was a president.}
		\symbol{D}{Mondale was a president.}
		\symbolization{A \land B \land C, \neg (A \land D) \therefore \neg (C \land D)}
	\end{statement}

	\begin{tableau}
		{ line no sep= 2cm, for tree={s sep'=10mm}, just sep= 1.5cm, for tree={s sep'=10mm}, }
		[A \land B \land C,                  just={Premise}
				[\neg (A \land D),               just={Premise}
						[C \land D,                  just={Negated Conclusion}
								[A,                      just={From 1}
										[B,                  just={From 1}
												[C,              just={From 1}
														[D,          just={From 3}
																[\neg A, close, just={From 2} ]
																[\neg D, close]
														]
												]
										]
								]
						]
				]
		]
	\end{tableau}


	\begin{statement}{Notre Dame is clearly not unbeatable, since they are clearly beatable}
		\symbol{A}{Notre Dame is beatable}
		\symbolization{A \therefore \neg \neg A}
	\end{statement}
	\begin{tableau}
		{
			% begin tree preamble
			line no sep= 2cm,
			% distance of tree from line numbers
			for tree={s sep'=10mm},
			% control horizontal spread of branches
		}
		% end tree preamble
		[A, just={Premise}
				[\neg A, close, just={Negated Conclusion}]
		]
	\end{tableau}


	\begin{statement}{I will do logic without taking tests. So, I am not taking tests.}
		\symbol{A}{I will do logic}
		\symbol{B}{I will take tests}
		\symbolization{A \land \neg B \therefore \neg B}
	\end{statement}
	\begin{tableau}
		{ line no sep= 2cm, for tree={s sep'=10mm}, just sep= 1.5cm, for tree={s sep'=10mm}, }
		[A \land \neg B,             just={Premise}
				[B,                      just={Negated Conclusion}
						[A,                  just={From 1}
								[\neg B, close, just={From 1} ]
						]
				]
		]
	\end{tableau}

\end{enumerate}
% \end{document}
